Long name of the paper

### 2018-10-16 anzjs2018/sections/02_gtfs.tex
Figures for network and pf

One solution would be to use information obtained from
vehicles servicing other routes but traveling along the same roads
to estimate arrival times;
however, there is no direct way of knowing which routes share common roads.
Here we propose using an algorithm to convert the raw GTFS shape files
into a \emph{road network},
as demonstated in Figure~\ref{fig:network_creation}.
This involves detecting locations where one or more routes meet 
(intersections or \emph{nodes}),
and the connecting paths (road segments or \emph{edges}).
However, in this paper we use bus stops as nodes and the routes between them as edges.
This captures most overlaps, 
with the exception of some express services and multiple-stop locations,
but these are typically in high traffic areas and should be OK.
Figure~\ref{fig:nw_construct} demonstrates how several overlapping routes 
are merged to form a road network.
In section~\ref{sec:kf} we present a model for estimating veihcle travel time
along a road segment.

>>>>

One solution would be to use information obtained from
vehicles servicing other routes but traveling along the same roads
to estimate arrival times;
however, there is no direct way of knowing which routes share common roads.
Here we propose using an algorithm to convert the raw GTFS shape files
into a \emph{road network},
as demonstated in Figure~\ref{fig:network_creation}.
This involves detecting locations where one or more routes meet 
(intersections or \emph{nodes}),
and the connecting paths (road segments or \emph{edges}).
However, in this paper we use bus stops as nodes and the routes between them as edges.
This captures most overlaps, 
with the exception of some express services and multiple-stop locations,
but these are typically in high traffic areas and should be OK.
Figure~\ref{fig:network_creation_2} demonstrates how several overlapping routes 
are merged to form a road network.
In section~\ref{sec:kf} we present a model for estimating veihcle travel time
along a road segment.

\begin{figure}[tb]
    \centering
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/02_network_segments_1.pdf}
        \caption{Raw GTFS route shapes}
        \label{fig:network_creation_1}
    \end{subfigure} \\
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/02_network_segments_2.pdf}
        \caption{GTFS-based road network}
        \label{fig:network_creation_2}
    \end{subfigure}
    \caption{Construction of a route network involves combining routes at nodes %
        (here we are using stops) which are connected by edges (roads). %
        In (a), the three unique routes, represented by different line types, clearly %
        overlap in several places. In (b) these have been merged, and the width of each line %
        represents how many routes use that link.}
    \label{fig:network_creation}
\end{figure}

### 2018-10-16 anzjs2018/sections/03_models.tex
Figures for network and pf

In the particle filter, the posterior distribution of the state at time $t_{k-1}$,
is represented by a set of discrete points, or particles, (fig~\ref{fig:pf_state_prev})
\begin{equation}
p(\bX_{k-1} | \bY_{k-1}) \approx \tilde\bX_{k-1|k-1} := (\bX_{k-1}^{(i)})_{i=1}^N
\end{equation}
each of which is independently updated or \emph{mutated} using the transition function $f$ (fig~\ref{fig:pf_state_predict})
\begin{equation}
p(\bX_k | \bX_{k-1}) \approx \tilde\bX_{k|k-1} := 
\left(f(\bX_{k-1}^{(i)}, \psi)\right)_{i=1}^N
\end{equation}
using a parameter vector $\psi$ containing all of the necessary parameters
for the model (including system noise).
After mutation, \emph{selection} of a new set of particles is performed by
importance resampling using likelihood weights,
determined by distance between particle's map position and $\bY_k$ (fig~\ref{fig:pf_state_map})
to obtain a new sample $\tilde\bX_{k|k}$, (fig~\ref{fig:pf_state_update}).

>>>>

In the particle filter, the posterior distribution of the state at time $t_{k-1}$,
is represented by a set of discrete points, or particles, (fig~\ref{fig:pf_state_prev})
\begin{equation}
p(\bX_{k-1} | \bY_{k-1}) \approx \tilde\bX_{k-1|k-1} := (\bX_{k-1}^{(i)})_{i=1}^N
\end{equation}
each of which is independently updated or \emph{mutated} using the transition function $f$ (fig~\ref{fig:pf_state_predict})
\begin{equation}
p(\bX_k | \bX_{k-1}) \approx \tilde\bX_{k|k-1} := 
\left(f(\bX_{k-1}^{(i)}, \psi)\right)_{i=1}^N
\end{equation}
using a parameter vector $\psi$ containing all of the necessary parameters
for the model (including system noise).
After mutation, \emph{selection} of a new set of particles is performed by
importance resampling using likelihood weights,
determined by distance between particle's map position and $\bY_k$ 
to obtain a new sample $\tilde\bX_{k|k}$, (fig~\ref{fig:pf_state_update}).

\begin{figure}[tb]
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/03_particle_filter_1.pdf}
        \caption{The vehicle state represented by a sample of discrete points is related to the observable state (GPS position) through the transition function $h$.}
        \label{fig:pf_state_prev}
    \end{subfigure}\;\;
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/03_particle_filter_2.pdf}
        \caption{The transition function $f$ models the behaviour of each particle,
            including changes in acceleration and stopping behaviour at bus stops.}
        \label{fig:pf_state_predict}
    \end{subfigure}\\
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/03_particle_filter_6.pdf}
        \caption{Each particle's distance from the true observation is calculated using
            the geographic distance between two coordinates, which can then be used
            to calculate it's weight.}
        \label{fig:pf_state_update}
    \end{subfigure}\;\;
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/03_particle_filter_4.pdf}
        \caption{Resampling occurs using likelihood weights that use the distance
            between the particle's location and the vehicles reported location (red cross),
            resulting in the updated state.}
        \label{fig:pf_state_predict2}
    \end{subfigure}
    \caption{The vehicles state is estimated using a set of discrete points, or particles,
        each of which is independently mutated to make predictions of the future state. The history of the state estimates can be used to estimate parameters of interest, such as
        travel times along roads.}
    \label{fig:pf_state}
\end{figure}
